### 2021-10-05 analysis/fit_models.Rmd
reorganised the code structures and stated exploring how the proportion of scouts varies accross landscapes.

@@

ggsave(
  plot = aic_plot,
  filename = "analysis/figures/AIC_plot.png",
  width = 90,
  height = 110,
  units = "mm",
  dpi = 300
)

@@

ggsave(
  plot = ks_plot_dist,
  filename = "analysis/figures/sites_ks.png",
  width = 86,
  height = 180,
  units = "mm",
  dpi = 300
)

ggsave(
  plot = all_sites$STU$fit,
  filename = "analysis/figures/STU.png",
  width = 90,
  height = 110,
  units = "mm",
  dpi = 300
)

ggsave(
  plot = all_sites$ZSL$fit,
  filename = "analysis/figures/ZSL.png",
  width = 90,
  height = 110,
  units = "mm",
  dpi = 300
)
```

@@

ggsave(
  plot = merge_plot,
  filename = "analysis/figures/site_map.png",
  width = 90,
  height = 110,
  units = "mm",
  dpi = 300
)

@@

ggsave(
  plot = sites_model_plot,
  filename = "analysis/figures/sites_model_plot.png",
  width = 183,
  height = 190,
  units = "mm",
  dpi = 300
)
```

@@

ggsave(
  plot = merge_plot,
  filename = "analysis/figures/site_map.png",
  width = 183,
  height = 190,
  units = "mm",
  dpi = 300
)

@@

ggsave(
  plot = sites_model_plot,
  filename = "analysis/figures/results_model_plot.png",
  width = 183,
  height = 190,
  units = "mm",
  dpi = 300
)
```

>>>>

# save results
saveRDS(df, file = "analysis/results/site_fit_results.Rda")

@@

ggsave(
  plot = aic_plot,
  filename = "analysis/results/figures/AIC_plot.png",
  width = 90,
  height = 110,
  units = "mm",
  dpi = 300
)

@@

ggsave(
  plot = ks_plot_dist,
  filename = "analysis/results/figures/sites_ks.png",
  width = 86,
  height = 180,
  units = "mm",
  dpi = 300
)

ggsave(
  plot = all_sites$STU$fit,
  filename = "analysis/results/figures/STU.png",
  width = 90,
  height = 110,
  units = "mm",
  dpi = 300
)

ggsave(
  plot = all_sites$ZSL$fit,
  filename = "analysis/results/figures/ZSL.png",
  width = 90,
  height = 110,
  units = "mm",
  dpi = 300
)
```

@@

ggsave(
  plot = merge_plot,
  filename = "analysis/results/figures/site_map.png",
  width = 90,
  height = 110,
  units = "mm",
  dpi = 300
)

@@

ggsave(
  plot = sites_model_plot,
  filename = "analysis/results/figures/sites_model_plot.png",
  width = 183,
  height = 190,
  units = "mm",
  dpi = 300
)
```

@@

ggsave(
  plot = merge_plot,
  filename = "analysis/results/figures/site_map.png",
  width = 183,
  height = 190,
  units = "mm",
  dpi = 300
)

@@

ggsave(
  plot = sites_model_plot,
  filename = "analysis/results/figures/results_model_plot.png",
  width = 183,
  height = 190,
  units = "mm",
  dpi = 300
)
```
